raptr: Representative and Adequate Prioritisation Toolkit in R

### 2016-09-30 code/rmarkdown/article.Rmd
+ assorted changes

```{r, include=FALSE}
## initialization
# load .rda file
checkpoint::checkpoint('2016-07-25', R.version='3.3.1', scanForPackages=FALSE)
try(session::restore.session('data/final/results.rda'))

# set options
options(error=NULL)

@@

# Data accessibility
The \texttt{raptr R} package can be downloaded from The Comphrehensive R Archive Netowrk (\url{https://cran.r-project.org/}). All data, code, and results are stored in an online repository (\url{www.github.com/paleo13/raptr-manuscript}) to permit replication and validation of this study.

>>>>

```{r, include=FALSE}
## initialization
# load .rda file
checkpoint::checkpoint('2016-07-25', R.version='3.3.1', scanForPackages=FALSE)
session::restore.session('data/final/results.rda')

@@

# Data accessibility
The \texttt{raptr R} package can be downloaded from The Comphrehensive R Archive Network (\url{https://cran.r-project.org/}). All data, code, and results are stored in an online repository (\url{www.github.com/paleo13/raptr-manuscript}) to permit replication and validation of this study.
